Measurement Bias from Address Aliasing

### 2016-05-15 presentation.tex
Start on a picture of sliding window

\usetikzlibrary{patterns,shapes,positioning,calc}
\setbeamertemplate{bibliography item}[text]
\lstset{language=C, basicstyle=\ttfamily\scriptsize, columns=flexible, belowskip=0pt, aboveskip=-1pt}

@@

\begin{frame}
  \frametitle{How to Measure Aliasing}
  \framesubtitle{Using Hardware Performance Counters}

  % Some points on hardware perf counters.
  \begin{itemize}
    \item Using processor-specific instrumentation, we can \emph{count} various low-level events during execution.
    \item Intel manual lists hundreds of events.
  \end{itemize}

@@

@@

  \begin{frame}
    \frametitle{Optimization Resistant Code}

    % Convolution example code

>>>>

\usetikzlibrary{patterns,shapes,positioning,calc}
\setbeamertemplate{bibliography item}[text]
\lstset{language=C, basicstyle=\ttfamily\scriptsize, columns=flexible, belowskip=0pt, aboveskip=0pt}

@@

% More generic on methodology? Not necessary for presentation maybe..
% Just to straight to the juice.
\begin{frame}
  \frametitle{How to Measure Address Aliasing}
  \framesubtitle{Using Hardware Performance Counters}

  % Some points on hardware perf counters.
  \begin{itemize}
    \item Control execution environment (disable ASLR).
    \item Using processor-specific instrumentation, we can \emph{count} various low-level events during execution.
      \begin{itemize}
        \item Cycles executed, branch prediction misses, instructions fetched, etc.
      \end{itemize}
    %\item Intel manual lists hundreds of events.
  \end{itemize}

  Events covering 4K aliasing:

@@

    \begin{itemize}
      \item Alias conflicts can happen between any sections of memory.
      \item While stack addresses depend on environment, heap addresses depend on allocators.
    \end{itemize}

    Looked at several allocators:

    \begin{itemize}
      \item ptmalloc (glibc)
      \item tcmalloc (Google)
      \item jemalloc
      \item Hoard
    \end{itemize}

@@

\begin{frame}[fragile]
  \frametitle{mmap}

    Most allocators use anonymous memory mapping for large allocations.

\begin{lstlisting}[frame=single, xleftmargin=.01\textwidth, xrightmargin=.01\textwidth]
$ man mmap

(...) on Linux, the mapping will be created at a nearby page boundary.
The address of the new mapping is returned as the result of the call.

\end{lstlisting}

\begin{frame}[fragile]
  \frametitle{Optimization Resistant Code}

% Image of sliding window with buffers in and out (Color variables?)

\begin{tikzpicture}[
  barstyle/.style={rectangle,fill=lightgray,draw,anchor=center,minimum width=9cm}
]
\node [barstyle] (in) at (0,1) { } ;
\node [barstyle] (out) at (0,0) { } ;
\node [rectangle,draw,minimum height=1.8cm] (bar) at (-2,0.5) { } ;

\node[] (input label) [left=of in] { in } ;
\node[] (output label) [left=of out] { out } ;

\draw[->] (-2,0.5) -- (-1.5,0.5) node [right,align=center] {\scriptsize{Sliding window}} ;

\end{tikzpicture}

% Convolution example code
\begin{figure}[t]
  \lstinputlisting[
    language=C,
    frame=single,
    xleftmargin=.00\textwidth,
    xrightmargin=.00\textwidth
  ]{bin/convolution-kernel.c}
  \caption{Simplified implementation of convolution with a fixed kernel. This program is highly sensitive to aliasing between input and output arrays, continuously generating false dependencies.}
  \label{lst:conv}
\end{figure}
